---
title: "Demonstrating The LLN and CLT"
output: html_notebook
---
```{r}
rm(list=ls())
gc()

library(tidyverse)
library(skimr)
```

# Generating Draws from a Target Distribution

Let's generate some uniform random numbers.

```{r}
u <- runif(1000)
ggplot(data=as.tibble(u),aes(x=u)) + geom_density()
```

Now, we apply the inverse CDF trick to get random numbers from a desired distribution. We'll use the exponential distribution, which has the CDF
$$
F(x) = 1 - e^{-\lambda x}
$$
for given $\lambda > 0$. The inverse CDF is given by 
$$
x = G(p) = -\lambda^{-1}\log(1-p)
$$

Next, we need to define a function so that we can evaluate the inverse CDF $G(p)$.

```{r}
lambda = 1

inverseCDF <- function(p){
  x <- -log(1-p)/lambda
  return(x)
}
```

Let's confirm that when we apply the inverse CDF to the uniform random numbers, we do indeed get draws from our target distribution - in this case, the Exponential(1) distribution.

```{r}
# R understands how to apply user-defined functions to whole vectors of inputs
myX <- inverseCDF(u)
ggplot(data=as.tibble(myX),aes(x=myX)) + geom_density()
```

Now, we generate the draws from the sampling distribution. Note carefully what the inner loop (over $b$) does as opposed to the outer loop (over $n$).

```{r}

B = 1000

sample_sizes <- c(10, 100, 1000, 10000)
df <- as.tibble(data.frame(matrix(NA, nrow = B, ncol = length(sample_sizes))))
for (i in 1:length(sample_sizes)){
  colnames(df)[i] <- paste("n", sample_sizes[i], sep = "")
}

# set a seed for the (pseudo-) random number generator to ensure reproducibility
set.seed(03132019)

for (i in 1:length(sample_sizes)){
  for (b in 1:B){
      x <- inverseCDF(runif(sample_sizes[i]))
      df[b,i] <- mean(x)
      rm(x)
  }
}



```

Now that we have our $B$ draws from $\hat{\theta}_n$, we need to standardize them and plot the distributions.

```{r}

standardized_draws <- as.tibble(data.frame(matrix(NA, nrow = B, ncol = length(sample_sizes))))
for (i in 1:length(sample_sizes)){
  colnames(standardized_draws)[i] <- paste("z", sample_sizes[i], sep = "")
  standardized_draws[i] <- sqrt(sample_sizes[i])*(df[i] - 1)
}

# clean up
rm(sample_sizes)
```


